signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-19 paper.tex
improved plots

\documentclass[fleqn,10pt,twoside]{gcb15submission}
\usepackage{url}\urlstyle{same}
\usepackage{booktabs}
\usepackage{colortbl, xcolor}

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/reglen.png}
\caption{A) Distribution of lengths of signal peptides. B) Distribution of the lengths of signal peptide regions. The measure of the length is a number of amino acids in the subsequence. The data was extracted from 2~589 signal peptide sequences derived from UniProt database (see \textbf{Data selection} in \textbf{Methods}).}
\label{fig:reglen}
\end{figure}

@@

%model structure
\begin{figure}
 \begin{minipage}{.5\linewidth} 
     \resizebox{6.5cm}{!}{%
    \begin{tikzpicture}[->,>=stealth',shorten >=2pt,auto,node distance=4.5cm, thick]
    \label{fig:model_hsmm}
      \tikzstyle{line} = [draw=black, color=blue!30!black!50, line width=4.5mm, -latex']
      \tikzstyle{main node} = [circle,fill=blue!20,draw, minimum size = 2.2cm, font=\itshape,
         align=center,  top color=white, bottom color=blue!50!black!70 ] %font=\sffamily\small\bfseries,
      %nodes
      \node[main node]            (start') 	[]						{Start};	     
      \node[main node, bottom color=purple!70!black!70] 	(nregion') 	[right of=start',xshift=-5mm, yshift=15mm] 	{n-region};
      \node[main node, bottom color=pink!70!black!70] 	(hregion') 	[right of=nregion',xshift=-5mm,yshift=15mm] 	{h-region};
      \node[main node, bottom color=gray!70!black!70] 	(cregion') 	[right of=hregion',xshift=-5mm,yshift=-15mm] 	{c-region};
      \node[main node, bottom color=green!70!black!70] 	(mature') 	[right of=cregion',xshift=-5mm, yshift=-15mm] 	{Mature protein};

      %lines
      \path [line] (start')   edge node [left, color=black] {} (nregion');
      \path [line] (nregion') edge node [below, color=black] { } (hregion');
      \path [line] (hregion') edge node [below, color=black] { } (cregion');
      \path [line] (cregion') edge node [left, color=black] { } (mature');
      \draw [line] (start') to[out=340,in=200] (mature');
    \end{tikzpicture} }
    \caption{The diagram of signalHsmm.}
    \label{fig:signalHsmm}
\end{minipage}
 \begin{minipage}{.5\linewidth}
     \resizebox{6.5cm}{!}{%
    \begin{tikzpicture}[->,>=stealth',shorten >=2pt,auto,node distance=4.5cm, thick]
    \label{fig:model_hsmm_kMer}
      \tikzstyle{line} = [draw=black, color=blue!30!black!50, line width=4.5mm, -latex']
      \tikzstyle{main node} = [circle,fill=blue!20,draw, minimum size = 2.2cm, font=\itshape,
         align=center,  top color=white, bottom color=blue!50!black!70 ] %font=\sffamily\small\bfseries,
      %nodes
      \node[main node]            (start')   []  					{Start};	     
      \node[main node, bottom color=purple!70!black!70] 	(nregion') 	[right of=start',xshift=-25mm, yshift=35mm] 	{n-region};
      \node[main node, bottom color=pink!70!black!70] 	(hregion') 	[right of=nregion',xshift=-25mm,yshift=35mm] 	{h-region};
      \node[main node, bottom color=gray!70!black!70] 	(cregion') 	[right of=hregion',xshift=-10mm,yshift=-25mm] 	{c-region};
      \node[main node, bottom color=green!70!black!70] 	(mature') 	[below of=hregion',xshift=15mm, yshift=-90mm] 	{Mature protein};

      \node[main node, bottom color=yellow!70!black!70]   (kmer1) 	[below of=cregion',xshift=35mm,yshift=30mm] 	{Aminoacid 1};
      \node[main node, bottom color=yellow!70!black!70]   (kmer2) 	[below of=kmer1,xshift=-5mm,yshift=5mm] 	{Aminoacid 2};
      \node[main node, bottom color=yellow!70!black!70]   (kmer3) 	[below of=kmer2,xshift=-5mm,yshift=5mm] 	{Aminoacid 3};
      %lines
      \path [line] (start')   edge node [left, color=black] {} (nregion');
      \path [line] (nregion') edge node [below, color=black] { } (hregion');
      \path [line] (hregion') edge node [below, color=black] { } (cregion');
      \path [line] (cregion') to[out=230,in=90] (mature');
      \draw [line] (start') to[out=300,in=180] (mature');

@@

      %\draw [decorate,line width=3pt,decoration={brace,amplitude=10pt}] ([xshift=5mm, yshift=5mm]kmer1) -- ([yshift=-25mm]kmer3) node [black,midway,xshift=0.6cm] {\footnotesize $P_1$};
      \draw[decoration={brace,amplitude=10pt, raise=5pt},decorate, line width=2pt]  
      ([yshift=1mm]kmer1.east) -- ([yshift=-5mm]kmer3.east) node [black,midway,xshift=0.6cm] {\large \color{black!90} n-gram};
    \end{tikzpicture} }
    \caption{The diagram of signalHsmm extended with the n-gram cleavage site model.}
    \label{fig:ngramext}
    \end{minipage}
\end{figure}

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/cvres.png}
\caption{Sensitivity and specificity of encodings after cross-validation. 1. The encoding providing the best sensitivity (AUC = 0.9683, MCC = 0.8677). 2. The encoding providing the best specificity (AUC = 0.9338, MCC = 0.6474).}
\label{fig:cvres}
\end{figure}

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/enccomp.png}
\caption{A comparison of encodings. A) Properties of amino acids in the best and the worst sensitivity encoding. B) Frequencies of amino acids belonging to the encodings in regions of signal peptide and mature proteins.}
\label{fig:enccomp}
\end{figure}

>>>>

\documentclass[fleqn,10pt,twoside]{gcb15submission}
\usepackage{url}\urlstyle{same}
\usepackage{booktabs}
\usepackage{colortbl, xcolor}
\usepackage{epstopdf}

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/reglen.eps}
\caption{A) Distribution of lengths of signal peptides. B) Distribution of the lengths of signal peptide regions. The measure of the length is a number of amino acids in the subsequence. The data was extracted from 2~589 signal peptide sequences derived from UniProt database (see \textbf{Data selection} in \textbf{Methods}).}
\label{fig:reglen}
\end{figure}

@@

%model structure
\begin{figure}
 \begin{minipage}{.5\linewidth} 
     \resizebox{6.5cm}{!}{%
    \begin{tikzpicture}[->,>=stealth',shorten >=2pt,auto,node distance=4.5cm, thick]
    \label{fig:model_hsmm}
      \tikzstyle{line} = [draw=black, color=blue!30!black!50, line width=3mm, -latex']
      \tikzstyle{main node} = [circle,fill=blue!20,draw, minimum size = 2.2cm, font=\Large\itshape,
         align=center,  ] %font=\sffamily\small\bfseries,
      %nodes
      \node[main node]            (start') 	[]						{Start};	     
      \node[main node, fill=purple!80!black!40 ] 	(nregion') 	[right of=start',xshift=-5mm, yshift=15mm] 	{n-region};
      \node[main node, fill=orange!70!black!40] 	(hregion') 	[right of=nregion',xshift=-5mm,yshift=15mm] 	{h-region};
      \node[main node, fill=yellow!70!black!40] 	(cregion') 	[right of=hregion',xshift=-5mm,yshift=-15mm] 	{c-region};
      \node[main node, fill=green!70!black!40] 	(mature') 	[right of=cregion',xshift=-5mm, yshift=-15mm] 	{Mature protein};

      %lines
      \path [line] (start')   edge node [left, color=black] {} (nregion');
      \path [line] (nregion') edge node [below, color=black] { } (hregion');
      \path [line] (hregion') edge node [below, color=black] { } (cregion');
      \path [line] (cregion') edge node [left, color=black] { } (mature');
      \draw [line] (start') to[out=340,in=200] (mature');
    \end{tikzpicture} }
    \caption{The diagram of signalHsmm.}
    \label{fig:signalHsmm}
\end{minipage}
 \begin{minipage}{.5\linewidth}
     \resizebox{6.5cm}{!}{%
    \begin{tikzpicture}[->,>=stealth',shorten >=2pt,auto,node distance=4.5cm, thick]
    \label{fig:model_hsmm_kMer}
      \tikzstyle{line} = [draw=black, color=blue!30!black!50, line width=3mm, -latex']
      \tikzstyle{main node} = [circle,fill=blue!20,draw, minimum size = 2.2cm, font=\Large\itshape,
         align=center,  ]
      %nodes
      \node[main node]            (start')   []  					{Start};	     
      \node[main node, fill=purple!80!black!40] 	(nregion') 	[right of=start',xshift=-25mm, yshift=35mm] 	{n-region};
      \node[main node, fill=orange!70!black!40] 	(hregion') 	[right of=nregion',xshift=-15mm,yshift=35mm] 	{h-region};
      \node[main node, fill=yellow!70!black!40] 	(cregion') 	[right of=hregion',xshift=-10mm,yshift=-10mm] 	{c-region};
      \node[main node, fill=green!70!black!40] 	(mature') 	[below of=hregion',xshift=15mm, yshift=-110mm] 	{Mature protein};

      \node[main node, fill=green!50!red!60!black!20]   (kmer1) 	[below of=cregion',xshift=35mm,yshift=30mm] 	{Aminoacid 1};
      \node[main node, fill=green!50!red!60!black!20]   (kmer2) 	[below of=kmer1,xshift=-5mm,yshift=-5mm] 	{Aminoacid 2};
      \node[main node, fill=green!50!red!60!black!20]   (kmer3) 	[below of=kmer2,xshift=-5mm,yshift=-5mm] 	{Aminoacid 3};
      %lines
      \path [line] (start')   edge node [left, color=black] {} (nregion');
      \path [line] (nregion') edge node [below, color=black] { } (hregion');
      \path [line] (hregion') edge node [below, color=black] { } (cregion');
      \path [line] (cregion') to[out=230,in=90] (mature');
      \draw [line] (start') to[out=300,in=180] (mature');

@@

      %\draw [decorate,line width=3pt,decoration={brace,amplitude=10pt}] ([xshift=5mm, yshift=5mm]kmer1) -- ([yshift=-25mm]kmer3) node [black,midway,xshift=0.6cm] {\footnotesize $P_1$};
      \draw[decoration={brace,amplitude=10pt, raise=5pt},decorate, line width=2pt]  
      ([yshift=1mm]kmer1.east) -- ([yshift=-5mm]kmer3.east) node [black,midway,xshift=0.6cm] {\LARGE \color{black!90} n-gram};
    \end{tikzpicture} }
    \caption{The diagram of signalHsmm extended with the n-gram cleavage site model.}
    \label{fig:ngramext}
    \end{minipage}
\end{figure}

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/cvres.eps}
\caption{Sensitivity and specificity of encodings after cross-validation. 1. The encoding providing the best sensitivity (AUC = 0.9683, MCC = 0.8677). 2. The encoding providing the best specificity (AUC = 0.9338, MCC = 0.6474).}
\label{fig:cvres}
\end{figure}

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/enccomp.eps}
\caption{A comparison of encodings. A) Properties of amino acids in the best and the worst sensitivity encoding. B) Frequencies of amino acids belonging to the encodings in regions of signal peptide and mature proteins.}
\label{fig:enccomp}
\end{figure}
